A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-05-04 ionic_liquids.tex
intro e abstract

\title{A molecular dynamics study of the solvation of CO\textsubscript{2}, water, and some organic compounds in the ionic liquids [emim][B(CN)\textsubscript{4}] and [emim][NTf\textsubscript{2}]}

@@

\begin{abstract}
In this paper we predict solvation in ionic liquids and macroscopic properties required in the design of chemical processes. Carbon dioxide produced in combustion processes is one of the main sources of anthropogenic generation of greenhouse gases. On the other hand, the potential of [emim][B(CN)\textsubscript{4}] for its capture has recently been reported. For comparison, the solvents [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N] were analyzed, both in the condition of infinite dilution and at high concentrations. The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in [emim][B(CN)\textsubscript{4}] to obtain the same molality of CO\textsubscript{2}. The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in [emim][B(CN)\textsubscript{4}] were also calculated, and a comparison was made with experimental values recently reported in the literature.
\end{abstract}

\begin{keyword}
ionic liquids \sep solvation free energy \sep  CO\textsubscript{2} 
\end{keyword}

@@

\section{Introduction}
State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results. foreseeable future

The CO\textsubscript{2} emissions from power generation plants are still sources of anthropogenic greenhouse gases~\cite{totalenergy} and the searching of solvents is an active field of research. Post combustion absorption technologies flue gas

Basically, the conventional process for CO\textsubscript{2} removal involves a chemical absorption followed by stripping at high temperatures. The solvents commonly used are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA). Despite its high absorption capability, the use of MEA suffers from a serious drawback in that there is considerable cost due to the energy consumption in the solvent recovery~\cite{Merkel_2010}. Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes with ambient pollution and generates extra costs for substituting the solvent.

The investigation of ionic liquids (ILs) as alternative solvents for CO\textsubscript{2} sequestration occupies a central place. The reasons in their well known properties, such as the negligible vapor pressure and high thermal stability. Furthermore, they are particularly attractive because they can be designed for specific applications, giving rise to the so-called task-specific ionic liquids~\cite{Seo_2014}. These remarkable properties makes ionic liquids suitable for a wide variety of applications in separation processes~\cite{Han_2010,Werner_2010}, catalysis~\cite{P_rvulescu_2007}, energy~\cite{MacFarlane_2014} and material science~\cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.

Recently, the potentiality of ionic liquids for CO\textsubscript{2} capture has been called into question by Carvalho~\textit{et al.}~\cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ionic liquids. While most thermodynamic models are developed based on molar fraction, the key factor to determine the absorption process efficiency is given by the amount of CO\textsubscript{2} that can be dissolved in a certain volume or mass of solvent. By expressing the solubility in terms of molality and performing an exhaustive comparison between various ionic liquids, Ref.~\cite{Carvalho_2016} shows that most systems which promote a physical absorption of CO\textsubscript{2} exhibit a CO\textsubscript{2} solubility similar or even lower than that observed for the heavy alkane eicosane. This is true for the ``popular'' [bmim][Tf\textsubscript{2}N], [bmim][PF\textsubscript{6}], [bmim][BF\textsubscript{4}], as well as for those synthesized from the fluorination of the cation or the anion, such as [(C\textsubscript{2}H\textsubscript{2}F\textsubscript{2})mim][NTf\textsubscript{2}] and [hmim][pFAP], the only exception being the family of ionic liquids containing the anion tetracyanoborate [B(CN)\textsubscript{4}]$^{-}$.

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion [B(CN)\textsubscript{4}]$^{-}$, whether special interactions with CO\textsubscript{2} are settled. In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes. To our knowledge, only one study in the literature reports the free energy of solvation of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] which, in addition, is overestimated. This motivated us to carry out a comparison of different force fields of [emim][B(CN)\textsubscript{4}] in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of CO\textsubscript{2}. For comparison, the solvents [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N] were analyzed, both in the condition of infinite dilution and at high concentrations. The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in [emim][B(CN)\textsubscript{4}] to obtain the same molality of CO\textsubscript{2}. The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in [emim][B(CN)\textsubscript{4}] were also calculated, and a comparison was made with experimental values recently reported in the literature.

This paper is organized as follows: in Section~\ref{sec:theory} we present some methodological details, including the mathematical relationships between free energy of simulated solvation and thermodynamic properties of diluted solutions. and a brief description of the force fields considered for [emim][B(CN)\textsubscript{4}], and the details of the simulations for free energy calculations are presented. The corresponding results are presented in the Section~\ref{sec:results}, where a comparison is made with the experimental data of Henry's constants, the results of the activity coefficients are shown at infinite dilution and, finally, a study of the CO\textsubscript{2} solvation is carried out in high concentrations.

@@

In this section, we present the formalism that allows a direct comparison between simulation results and the thermodynamic properties of dilute solutions: Henry constant and activity coefficient at infinite dilution. For this, we rely on the work of Shirts~\textit{et al.}~\cite{Shirts_2003}. Then, we reformulate the equations in order to carry out a study at concentrated conditions, which would be the more likely scenario in CO\textsubscript{2} capture processes.

@@

Considering $N_s^{l}$ = 1, which represents the infinite-dilute condition, and substituting Eqs.~\ref{eq:mu_res} and~\ref{eq:mu_res_0} into Eq.~\ref{eq:gamma}, we  obtain that
\begin{equation}
\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
\end{equation}
where $c_{\scaleto{LI}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ correspond to the numerical densities of the solvent and the pure solute, respectively.

\subsection*{Partial pressure estimation}

For the ILs of interest to the present investigation, high concentrations of CO\textsubscript{2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid. In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
\end{equation}
where $\phi_s$ is the fugacity coefficient of the solute. This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase. Having calculated $f^{g}_s$, $P_s$ could be predicted using the following equation
\begin{equation}
\label{eq:fgas}
f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
\end{equation}
where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for CO\textsubscript{2} introduced by Holste~\textit{et al}~\cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = $-2.455297$ $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol). Actually, the prediction of $P_s$ should be iterative and in this work we propose the following scheme: (i) run an NPT simulation, (ii) calculate $\Delta G_{\text{sim}}$ and $f^{g}_s$ via Eq.~\ref{eq:fgas_d}, (iii) employ $f^{g}_s$ in Eq.~\ref{eq:fgas} to compute $P_s$ (iv) if $P_s$ $\neq$ P, repeat the above steps using $P_s$ as the specified pressure in a new NPT simulation. This is done until $P_s$ = P.

@@

In this paper, we consider four models of [emim][B(CN)\textsubscript{4}]. Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of [emim][B(CN)\textsubscript{4}]. They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ and $\text{CH}_2$ of [emim]$^{+}$ are replaced by pseudo-atoms. Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity. In short, both the intramolecular and Lennard-Jones parameters of the cation were taken from the work of Liu~\textit{et al.}~\cite{Liu_2006}, which in turn is based on the AMBER~\cite{Cornell_1995} framework. The intramolecular parameters involving the boron atom were extracted from the DREIDING~\cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price~\textit{et al.}~\cite{Price_2001}. The atomic partial charges were derived using the EA-RESP method~\cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6–31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426e.

The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of [emim][B(CN)\textsubscript{4}]. In this case,  the authors considered the \textit{all-atom} model of [emim]$^{+}$ developed by Cadena and Maginn \cite{Cadena_2006}. The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions. It should be noted that those force fields consider different scaling factors for 1-4 non-bonded interactions: Cadena and Maginn \cite{Cadena_2006} use values of 1.0 y 0.4 for the Lennard-Jones and Coulombic interactions, respectively, while in Koller \textit{et al.} \cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with AMBER force field. Batista \textit{et al.} \cite{Batista_2015} employ the same factors as Cadena and Maginn \cite{Cadena_2006} (J.P. Coutinho, personal communication).

Another set of parameters for \mbox{[emim][B(CN)\textsubscript{4}]} was derived by Liu \textit{et al.}\cite{Liu_2014} in a study that investigates the dynamics of CO\textsubscript{2} and N\textsubscript{2} in that IL. Parameters corresponding to the intramolecular and Lennard-Jones interactions were extracted from GAFF~\cite{Wang_2004}, while the atomic partial charges were computed using the RESP method~\cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations. The net charges of the ions were manually adjusted to a value of $\pm$0.8$e$.

We also consider the parametrization recently reported by Weber and Kirchner~\cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}. The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}. The atomic partial charges were derived using the RESP procedure from \textit{Hartree-Fock} calculations at 6-31++G$^{\ast \ast}$ level of theory, resulting in net charges of $\pm$0.8$e$.

Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which result from refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}. This refining was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values. This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant for CO\textsubscript{2} at several temperatures.

@@

The solutes considered here are hexane, benzene, CO\textsubscript{2}, ethanol, cyclohexane and water. Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and CO\textsubscript{2}. Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005}, \cite{Vega_2011}.

@@

In this section, we present and compare the results obtained for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums~\cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method~\cite{Fennell2006} for calculating the Coulombic interactions.

First, we describe the approach for defining the rigid bodies. For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in [emim]$^{+}$ and [Tf\textsubscript{2}N]$^{-}$. On the other hand, small and highly symmetric anions, such as PF\textsubscript{6} and BF\textsubscript{4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\textsubscript{4}]$^{-}$. The atomic nomenclatureare adopted in this paper is shown in Fig~\ref{fig:atoms_id}. In the \textit{united-atoms} version of [emim]$^{+}$, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.

Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs. The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyze the rigidity of the ring. In Fig.~\ref{fig:dihedrals_emim} we present the results of the CDF for each model.

A first inspection of Fig. reveals a similar behavior of the models of [emim]$^{+}$ due to Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}. This was expected as both were developed based on the AMBER force field. In addition, Figs.(a) and(b) are symmetric, which means that atoms C1-N2-C2 are coplanar. Koller is the most rigid model, with The most likely angles in Fig.~(a) can be found in a narrow region around 90 and 270. Given that these angles correspond to the same configuration in the \textit{united-atom} version, we build all the rigid bodies specifying 90 for the dihedral angle of C5-C5-N2-C1. The other models present a larger flexibility of the ethyl chain, with high probability regions that extend  ina broad of angle values. However, in the case of Liu and Batista, it was possible to the following approach: we consider the most likely angles as obtained by the indificual histogram of the dihedral C5-C5-N2-C1, which were employed to construct two types of rigid bodies. In the case of Liu , 50 of the rigid bodies were build specifying the angle of 90 for the dihedral C6-C5-N2-C1 and -90 of the others. For Batista, we employed the angles 102.6  and -102.6 for buildign both types for rigid bodies in an equal proportion.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
\label{fig:atoms_id}
\end{figure}

@@

\subsection{Henry constant of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N]}
\label{sec:henry_results}

>>>>

\title{A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}

@@

\begin{abstract}
In this paper we calculate solvation free enegies in ionic liquids and predict macroscopic properties required in the design of chemical processes. Carbon dioxide produced in combustion processes is one of the main sources of anthropogenic generation of greenhouse gases. On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported. For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations. The simulations confirmed what was observed experimentally, namely the pressure required to obtain the same molality of \ce{CO_2} is notably lower in \ce{[emim][B(CN)_4]}. The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in literature.
\end{abstract}

\begin{keyword}
ionic liquids \sep solvation free energy \sep  \ce{CO_2} 
\end{keyword}

@@

\section{Introduction}

The \ce{CO_2} emissions from power generation plants are still an important source of anthropogenic greenhouse gases \cite{totalenergy}. International efforts aimed at regulating and reducing \ce{CO_2} emissions are increasing \cite{Tong_2018} and, in this context, the development of technologies for the capture and storage of \ce{CO_2} is essential. \cite{Markewitz_2014}.

The conventional process for \ce{CO_2} removal involves a chemical absorption followed by stripping at high temperatures. The solvents commonly employed are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA). Despite its high absorption capability, the use of MEA suffers from a serious drawback, namely a considerable cost due to the energy consumption of solvent recovery \cite{Merkel_2010}. Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the ambient pollution and generates extra costs to replace the solvent.

The use of ionic liquids (ILs) as solvents for \ce{CO_2} sequestration occupies a central place in the investigation of alternative technologies. The reasons are their well known properties, such as the negligible vapor pressure and high thermal stability. Furthermore, they are particularly attractive because they can be designed for specific applications, giving rise to the so-called task-specific ILs \cite{Seo_2014}. These remarkable properties makes ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy \cite{MacFarlane_2014} and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.

Recently, the potentiality of ILs for the \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs. While most thermodynamic models were developed based on molar fraction, the key factor to determine the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain volume or mass of solvent. By expressing the solubility in terms of molality and performing an exhaustive comparison between various ILs, Ref. \cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a \ce{CO_2} solubility similar or even lower than that observed for the heavy alkane eicosane. This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}, the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-]}.

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion \ce{[B(CN)_4]^-]}, whether special interactions with \ce{CO_2} are settled. In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes. To our knowledge, only one study in the literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated. This motivated us to carry out a comparison of different force fields of \ce{[emim][B(CN)_4]} in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of \ce{CO_2}. For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations. The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in \ce{[emim][B(CN)_4]} to obtain the same molality of \ce{CO_2}. The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in the literature.

This paper is organized as follows: in Sec. \ref{sec:theory} we present the mathematical relationships between the simulated solvation free energy and thermodynamic properties. This is followed by a brief description of the force fields considered for the ILs and the solutes. The methodological details are provided in Sec. \ref{sec:sim_details} and the numerical results are given in Sec. \ref{sec:results}. Finally, we present some concluding remarks in Sec. \ref{sec:conclusion}.

@@

In this section, we present the formalism that allows a direct comparison between simulation results and the thermodynamic properties of dilute solutions: Henry constant and activity coefficient at infinite dilution. For this, we rely on the work of Shirts \textit{et al.} \cite{Shirts_2003}. Then, we reformulate the equations in order to carry out a study at concentrated conditions, which would be the more likely scenario in \ce{CO_2} capture processes.

@@

Considering $N_s^{l}$ = 1, which represents the infinite-dilute condition, and substituting Eqs.~\ref{eq:mu_res} and~\ref{eq:mu_res_0} into Eq.~\ref{eq:gamma}, we  obtain that
\begin{equation}
\label{eq:gamma_inf}
\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
\end{equation}
where $c_{\scaleto{LI}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ correspond to the numerical densities of the solvent and the pure solute, respectively.

\subsection*{Partial pressure estimation}
\label{sec:partial_pressure}

For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid. In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
\end{equation}
where $\phi_s$ is the fugacity coefficient of the solute. This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase. Having calculated $f^{g}_s$, $P_s$ could be predicted using the following equation
\begin{equation}
\label{eq:fgas}
f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
\end{equation}
where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for \ce{CO_2} introduced by Holste~\textit{et al}~\cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = $-2.455297$ $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol). Actually, the prediction of $P_s$ should be iterative and in this work we propose the following scheme: (i) run an NPT simulation, (ii) calculate $\Delta G_{\text{sim}}$ and $f^{g}_s$ via Eq.~\ref{eq:fgas_d}, (iii) employ $f^{g}_s$ in Eq.~\ref{eq:fgas} to compute $P_s$ (iv) if $P_s$ $\neq$ P, repeat the above steps using $P_s$ as the specified pressure in a new NPT simulation. This is done until $P_s$ = P.

@@

In this paper, we consider four models of \ce{[emim][B(CN)_4]}. Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of \ce{[emim][B(CN)_4]}. They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ and $\text{CH}_2$ of \ce{[emim]^+} are replaced by pseudo-atoms. Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity. In short, both the intramolecular and Lennard-Jones parameters of the cation were taken from the work of Liu~\textit{et al.}~\cite{Liu_2006}, which in turn is based on the AMBER~\cite{Cornell_1995} framework. The intramolecular parameters involving the boron atom were extracted from the DREIDING~\cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price~\textit{et al.}~\cite{Price_2001}. The atomic partial charges were derived using the EA-RESP method~\cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6–31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426e.

The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}. In this case,  the authors considered the \textit{all-atom} model of \ce{[emim]^+} developed by Cadena and Maginn \cite{Cadena_2006}. The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions. It should be noted that those force fields consider different scaling factors for 1-4 non-bonded interactions: Cadena and Maginn \cite{Cadena_2006} use values of 1.0 y 0.4 for the Lennard-Jones and Coulombic interactions, respectively, while in Koller \textit{et al.} \cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with AMBER force field. Batista \textit{et al.} \cite{Batista_2015} employ the same factors as Cadena and Maginn \cite{Cadena_2006} (J.P. Coutinho, personal communication).

Another set of parameters for \mbox{\ce{[emim][B(CN)_4]}} was derived by Liu \textit{et al.} \cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and N\textsubscript{2} in that IL. Parameters corresponding to the intramolecular and Lennard-Jones interactions were extracted from GAFF~\cite{Wang_2004}, while the atomic partial charges were computed using the RESP method~\cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations. The net charges of the ions were manually adjusted to a value of $\pm$0.8$e$.

We also consider the parametrization recently reported by Weber and Kirchner \cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}. The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}. The atomic partial charges were derived using the RESP procedure from \textit{Hartree-Fock} calculations at 6-31++G$^{\ast \ast}$ level of theory, resulting in net charges of $\pm$0.8$e$.

Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which result from refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}. This refining was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values. This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant for \ce{CO_2} at several temperatures.

@@

The solutes considered here are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water. Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}. Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005}, \cite{Vega_2011}.

@@

In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums~\cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method~\cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions. For both strategies we employed $r_c$ = 12 {\AA}.

First, we describe the approach for building the rigid bodies. For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[Tf_2N]^-}. On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\ce{4}]$^{-}$. The atomic nomenclature adopted in this paper is shown in Fig~\ref{fig:atoms_id}. In the \textit{united-atoms} version of \ce{[emim]^+}, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{\ce{[emim]^+} [B(CN)\textsubscript{4}]$^{-}$ \ce{[NTf_2]^-}.}
\label{fig:atoms_id}
\end{figure}

Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtained the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs. The CDF, as an alternative to individual histograms, provides a way to  simultaneously analyze the rigidity of the ring. In Fig.~\ref{fig:dihedrals_emim} we present the results for each model of \ce{[emim][B(CN)_4]}.

A first inspection of Fig.~\ref{fig:dihedrals_emim} reveals a similar behavior of the models of \ce{[emim]^+} due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}. This was expected as both were developed based on the AMBER force field ~\cite{Cornell_1995}. In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar. In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$. Given that these angles correspond to the same configuration in the \textit{united-atom} representation of \ce{[emim]^+}, we built all the rigid bodies specifying the value of 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1. The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values. Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles for C6-C5-N2-C1. In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$. In these cases, two types of rigid bodies were built in equal proportion. Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models. In this case we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.

In Table~\ref{table:props_dsf} we show the results of density for the strategies mentioned at the begining of this section. When comparing the cases (1) and (2) for each model, we observe that the density values practically do not differ. In addition, the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental density. The model due to Weber and Kirchner also presents a small deviation of 1\%.

For the simulation strategies (1) and (2) we have also compared the results of relevant radial distribution functions (RDFs), which can be found in the Supplementary material. The better agreement was found for the force fields due to Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}. Even though the model of Liu \textit{et al.} \cite{Liu_2014} presented small deviations, the simulation with rigid bodies qualitatively reproduced the RDFs obtained for flexible ions. Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion). The model of Weber and Kirchner \cite{Weber_2016}, 
on the other hand, presented important discrepancies in the RDFs for the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies. That is why in this case we have considered as being rigid only the imidazolium ring while letting  the ethyl chain flexible.

@@

\subsection{Henry constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
\label{sec:henry_results}

For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results corresponding to the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}. Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}. The uncertainties were calculated using standard error propagation.
